Completing Programs with Relational Types

### 2023-11-28 paper/relationaltypes.tex
edit a little on spelling and wording about inherited types

Propagating types downward over a top-down parse-tree results in a varying interpretations of the downwardly propagated type used for local guidance.
For syntax that represents complete expressions, e.g. \[ :uno @ \], the inherited type represents the expected type for that expression.
However, for syntax that cannot represent a complete expression, the inherited type must represent something else. 
For instance, in the parse tree for a chain of projections, a syntactic subtree of projections, such as \[ .dos.tres \] does not constitute a complete expression.   
There is no type for this syntax. Thus, the inherited type represents the type that \[ .dos \] is expected to project from (or cut into), 
e.g. the descriptive type of \[ x.uno \].

@@

\subsection{Subtype Solving}
\TODO{type unification}
\TODO{econding to/decoding from horn clauses}

>>>>

Propagating types downward over a top-down parse-tree results in a varying interpretations of the downwardly propagated type used for local guidance.
For syntax that represents complete expressions, e.g. \[ x \], the inherited type represents the prescriptive type for that expression.
However, for syntax that cannot represent a complete expression, the inherited type must represent something else. 
For instance, in the parse tree for a chain of projections, a syntactic subtree of projections, such as \[ .dos.tres \] does not constitute a complete expression.   
There is no prescriptive type for this syntax. Thus, the inherited type represents the type that \[ .dos \] is expected to project from (or cut into), 
e.g. the descriptive type of \[ x.uno \].

@@

\subsection{Subtype Solving}
\TODO{type unification}
\TODO{encoding to/decoding from horn clauses}
